---
title: "Determinants of Exportation Types"
author: 
  - Filiz, Simge[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |Determinants of Exportation Types
This study has been created in order to find the positive or negative relationship between exportation and some certain factors. Regarding that releasing relation, my hyphothesis focuses on technological development and claims its obvious influence on the types of industry groups on exportation. To support that thesis,a correlation test was applied on selected products which are related to technologic levels of their own groups as being mid-tech and high-tech industries groups. In the result of that, the developed and developing countries, which are selected as sample, shows a different orientation regarding the technologic interest of them. So, the positive relationship that is supporting our hypothesis has occured and these result can have important roles in order to determine the way of countries' export share.
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 20080483, [Github Repo](https://github.com/simgefiliz/Final.git)

# Introduction
The relationship between growing status of countries and their trade facilities has been subject to many research. There can be found several determinants which directs that connection. To be more specific, exportation goods in a sector can be leveled or diversified regarding the passing years and the technological development of a country. In that sense, this study aims to reveal the effects of these factors and focus on one of them by analysing it in the methods and data analysis.  As a source, the data set was obtained from World Trade Organization and it has 59 countries’ observations with 12 variables in a period between 1990 and 2016. Most of the variables were categorized as representing the types of exportation products. To illuminate our results 6 different articles were examined and their graphs were demonstrated in following parts.

## Literature Review
One of the subgroups of globalization called exportation has gradual types of diffusion all around the world. The reasons for that distinction of goods’ qualities and values are the main purpose of our analysis and the answer for the research question. When we try to detail them through the articles and graphics that will be mentioned, it could be seen that there are several prominent factors such as the technological development of a country. Their effects create specific markets for every region on the process of exportation. 
To make clear these effects we will view the articles in a way of coming closer which ends with an example regarding the technological movements. Our first article gives us an example about the basic positive relationship between the productivity and the export variety. In figure 7, Japan has %50 more export variety than South Korea [@Feenstra:2004; @Kee:2004]. However, with the narrowing gap in productivity among them, the variety of Korea’s exportation starts to rise. When we look at our second article, the variety, or new products of a country is not taken into consideration as a main trigger for the export grown [@Zahler:2007]. Instead, a connection between new destinations for actual products and exportation growth has been created in the Table 1. From another research, we can deduce that agricultural safety standards of countries play an important role on determination of exports. For that, 4 main output structure are visualized in a bar chart by using the data collected from the countries that have 3 different kinds of socioeconomic status. These output structures of agriculture, processed foods, manufacturing and other goods exist in industrial, low-income and middle-income countries. According to that “Agriculture represents less than 2 percent of output for industrial countries and 10.5 percent for developing countries, while processed foods represent 4.5 percent for industrial countries and 7.5 percent for developing countries. Agriculture is still a relatively high 19 percent of output in the low-income developing countries.” [@Aksoy:2005; @Beghin:2005]. Those ratios are explained with a dependency of countries to food safety. While low-income countries’ importation is built on protected goods such as grains, their exportation has a tendency for less or no protected items. Next article offers another connection which argues that industrial analysis of a country’s exportation is suggestive to decide whether it is an industrial society or not. With the scale of Turkey, manufacturing industry forms the biggest part of that global trade between the years of 2000 and 2015 in the graph 2 [@Yenisu:2018]. That industry includes automotive, textile and ready-made clothing sectors and it can be easily said that Turkey is still an industrializing country even though mining and fuels exports has increased about 13.3 times. Eventually, this cause-and-effect relationship will be valid for the other countries.
When we went into detail and focused on the main determinant of our study, the next report and article contextualizes the technological improvement in years and its effect on the amount of the exportation in the manufacturing industry. In the Figure 5, first article demonstrates that export share of low-tech industries group in 1990, which is the dominant industry, has a share about 60% [@Saracoglu:2018]. Then, it shows a decreasing tendency until 2008 and ends up with %34 in 2017. On the other hand, the mid-low-tech and mid-high-tech industries groups, which started with 20%, reached a level of 30% export share. The last article has a proper table to look through those graded industries groups in the selected countries. However, different policies like specialization and product differentiation of that countries do not offer a one-to-one relationship between technological development and high-tech product exportation. In Figure 2, when we look at mid-tech industries Mexico, Brazil and South Korea show themselves as prominent countries. Also, high-tech products are concentrated in Singapore, Philippines and Malaysia because of MNC export-oriented operations [@Lall:2000]. In relation to that, the high-tech exportation facility of South Korea and Taiwan takes place with emphasis on domestic technological inputs and competence and these inputs are expected to be sold by MNC’s. So, more complex products that are transformed from inputs can be related with domestic technological development in an indirect way.


# Data
The data set as a source was a base for examining a kind of relationship between subjects of our study. In order to achieve this, the data was obtained from World Trade Organization and it has …. observations with 12 variables. The observations were determined among 59 countries and each variable displays character or double values such as types of exportation products and years.Exportation products vary in 10 groups and diffuse in the years between 1990 and 2016. To discuss it with a visual framework, the layout of the data set was shaped regarding the proper position of tidy sets and each variable has their own columns. In the next part, these values were analysed by applying method of correlation analysis and we came to the conclusion which highlights a relationship between the development level of countries and their amount of products to export. First of all, a table was created to understand main frame of variables. The table below demonstrates mean, standard deviation, minimum and maximum values. 

```{r}
library(tidyverse)
library(here)
DataWto5 <- read_xlsx(here("data/DataWto5.xlsx"))
```



```{r, echo=FALSE}
library(xtable) 
library(summarytools)
library(magrittr)
library(dplyr)
st_options(lang = "en")
```



```{r results='asis', echo=FALSE}
DataWto5 %>%
  select("Agricultural products", "Food", "Fuels and mining products", "Fuels", "Manufactures", "Iron and steel", "Chemicals", "Machinery and transport equipment", "Textiles", "Clothing") %>% 
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>% 
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>% 
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```


# Methods and Data Analysis
In order to put an emphasis on the differentiation of exportation regarding technological condition, 2 variables of each country as years and mid-tech, low-tech industries groups were selected. These groups include chemicals and textiles industries and Pearson correlation analysis were used to release the relationship between passing years which reacts to technology and the exportation share of a selected industry group. Turkey as a developing country and the United States of America with the developed status were chosen from the data set to be sample in this study. 
In the framework of Turkey, chemicals as mid-tech industries were analyzed in the years between 1990 and 2016. That analysis was showed in the correlation test below.
 
 
```{r}
library(ggplot2)
library("ggpubr")
library("dplyr")

DataWto5 <- read_xlsx(here("data/DataWto5.xlsx"))
DataWto5$Chemicals <- as.numeric(DataWto5$Chemicals)

DataWto5 <- read_xlsx(here("data/DataWto5.xlsx"))
DataWto5$Textiles <- as.numeric(DataWto5$Textiles)

filter(DataWto5, Chemicals > 80 & Textiles > 120) %>%
  filter(Country == 'Turkey') 


  ggscatter(DataWto5,
            x = 'Chemicals',
            y = 'Textiles',
            add = 'reg.line',
            add.params = list(color = 'blue'),
            conf.int = FALSE,
            cor.coef = TRUE,
            cor.coef.coord = c(25, 5),
            cor.method = 'pearson',
            ggtheme = theme_minimal())
  


```

When we look at the test, we can understand the type and size of the relation of variables by the blue line that was created on our graph. The correlation between 2 product groups are generally limited under 7 thousand of Chemicals and 1,5 thousand of Textiles.In that limited period, it can be said that there is a positive correlation between them. However, after that point, their correlation has been corrupted and they display small positive level of correlation with the increasing amount of the scale. This is the point where textiles started to climb up more than chemicals' ratio. So, when we try to interpret that, exportation share of mid-tech and low-tech industries are increasing together in that country, but mid-tech industry keeps its slow rise compared to low-tech one. In that case, technological interest of a country can be regarded as a factor in that amounts.

```{r}


DataWto5 %>% filter(Country == 'United States of America') 
DataWto5 %>% filter(Country == 'Turkey')

 

```

When we look at the 2 selected countries from the data set, Turkey showed a similar attitude with the general correlation of these targeted products. However, it is obvious that the USA put more weighted interest on chemicals industry which is mid-tech group.


# Conclusion

To sum, in our study we examined several determinants of exportation facility. The most predominant one in that analysis was technological relationship among them. Even some articles suggest that the policies and specialization factors have great influence in export share, our data analysis has put a claim the presence of some countries' interest on higher-tech industries groups. Also, until a some point countries can maintain  different kind of industries in exportation without giving up from one of them. These can be regarded as minor points of that factors to illuminate reasons behind the subject.

**_You shouldn't delete the last 3 lines. Those lines are required for References section._**

\newpage
# References {#references}
Feenstra, Kee. 2004. “Export Variety and Country Productivity”.  NBER Working Paper Series.
Zahler, Andres. 2007. “Decomposing world export growth and the relevance of new destinations”. Munich Personal RePEc Archive.
Aksoy, Beghin. 2005. “Global Agricultural Trade and Developing Countries”. The World Bank.
Yenisu, Ersin. 2018. “Export, Import and Economic Growth Relationship In Turkey: ARDL Bound Testing Approach”. GAUN JSS.
Lall, Sanjaya.2000. "The Technological Structure and Performance of Developing Country
Manufactured Exports, 1985-1998".Queen Elizabeth House, University of Oxford.
Saraçoğlu, Dürdane. 2018. "Üretim ve Dış Ticaret İlişkisi". T.C. Kalkınma Bakanlığı.
<div id="refs"></div>

