---
title: "Title"
author: 
  - Last Name, First Name[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    Write your abstract here.
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: Student ID, [Github Repo](https://github.com/YOUR_USER_NAME_HERE/YOUR_REPO_NAME_HERE)

# Important Information About Midterm

\colorbox{BurntOrange}{WRITE YOUR GITHUB REPO LINK ON LINE 37 IN THIS FILE!}

**Project Proposal submisson will be done by uploading a zip file to the ekampus system along with the Github repo link. If you do not upload a zip file to the system and do not provide a Github repo link, you will be deemed not to have entered the midterm and final exams.**

**You must upload your project folder (`YourStudentID.zip` file) to *ekampus.ankara.edu.tr* until 9 June 2023, 23:59.**

\colorbox{WildStrawberry}{Read the README.md file in the project folder for more information.}

# Introduction
This outline has been created to assist you in writing your project assignment. You should cite all the sources you use, articles, presentations, projects, etc. Quoting and referencing gives readers the opportunity to access the resources you refer. **Even though you use your own words, if you are conveying the ideas of others in your work, you have to document the source of these ideas. Otherwise, you are committing academic plagiarism.** For example, you can refer to @aydinonat:2007 for academic writing rules. You can find lots of online resources on this topic.

The sections in your project assignment should definitely include the sections in this text. Apart from the sections used here, you can use different subsections. When writing your project, use this file as a draft and adapt its content to your purposes.

In this section, mention the purpose and importance of your work in a few paragraphs.

## Literature Review

In this section, discuss the articles you have read on the subject by giving references. This is a narrative citation @chang:2013. This one is a parenthetical citation [@chang:2013]. **Do not summarize each article individually under a separate title.** In the literature review section, **at least six** articles must be cited [@newbold:2003; @verzani:2014; @wickham:2014; @wooldridge:2015a].

# Data
In this section, discuss the source of the data set you use in your study, if you have done any operation on the raw data, these operations and the summary statistics about the data set. In this section, it is mandatory to have a table (Table \ref{tab:summary}) containing summary statistics (mean, standard deviation, minimum, maximum, etc. values) of all variables. Make the necessary references to your tables as shown in the previous sentence [@perkins:1991].

R codes for the analysis should start in this section. In this section, you should include the codes that imports the data set into R and the codes that generate summary statistics.

```{r}
library(tidyverse)
library(here)
survey <- read_csv(here("data/survey.csv"))
```

Note that code options are edited in some of the code chunks in the Rmd file.

```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")
```

With the `echo=FALSE` option, prevent the codes from appearing in the derived pdf file and report your results in tables.

```{r results='asis', echo=FALSE}
survey %>%
  select("sex", "credits", "handedness", "height", "handspan") %>% 
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>% 
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>% 
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```


# Methods and Data Analysis
In this section describe the methods that you use to achieve the purpose of the study. You should use the appropriate analysis methods (such as hypothesis tests and correlation analysis) that we covered in the class. If you want, you can also use other methods that we haven't covered. If you think some method is more suitable for the purpose of the analysis and the data set, you can use that method [@newbold:2003; @verzani:2014; @wickham:2014; @wooldridge:2015a].

For example, if you are performing regression analysis, discuss your predicted equation in this section. Write your equations and mathematical expressions using $LaTeX$.

$$
Y_t = \beta_0 + \beta_N N_t + \beta_P P_t + \beta_I I_t + \varepsilon_t
$$

This section should also include different tables and plots. You can add histograms, scatter plots (such as Figure \@ref(fig:plot)), box plots, etc. Make the necessary references to your figures as shown in the previous sentence.


```{r plot, fig.align='center', fig.cap='An Awesome Plot'}
survey %>% 
  ggplot(aes(x = handedness, y = handspan)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous("Handedness") + 
  scale_y_continuous("Handspan")
```


# Conclusion
Summarize the results of your analysis in this section. Discuss to what extent your results responded to the research question you identified at the beginning and how this work could be improved in the future.

**References section is created automatically by Rmarkdown. There is no need to change the references section in the draft file.**

**_You shouldn't delete the last 3 lines. Those lines are required for References section._**

\newpage
# References {#references}
<div id="refs"></div>

